---
title: "Group 4 Appendix Code"
author: "MA 575 Group 4"
date: "4/29/2021"
output:
  html_document:
    df_print: paged
  html_notebook: default
  word_document: default
---

```{r setup}
# clear memory
rm(list = ls())

# pre-processing: includes loading libraries, splitting data, and handling variables
source("preprocessing.R")
```

## Figure 1: Plot of user types over time, 2011

```{r}
daily_users <- bikes_long %>% filter(year==0)
#create user type variable for graphing only
daily_users$usert <- ifelse(daily_users$user_type=="registered", 1,
                         ifelse(daily_users$user_type=="casual" & daily_users$workday==1, 2, 3))
table(daily_users$usert)

daily_user <- ggplot(daily_users, aes(date, user_rent, color=as.factor(daily_users$usert)) )+
  geom_point( size=0.5, alpha=0.8 ) +
  xlab("") +
  ylab("Daily Volume of Bike Rentals \n") +
  ggtitle("Bike Rentals Per Day in Washington DC by User Type, 2011") +
  scale_x_date(date_breaks = "2 months",  date_labels = "%b %Y", limits = as.Date(c('2010-12-31','2011-012-31'))  )+
  scale_color_manual(name = "User Types", labels=c( "Registered", "Casual \nWorkday", "Casual \nNon-Workday"), 
              values = c("indianred4",  "steelblue4", "steelblue3")) +
  stdplot 
 
daily_user
```

## Figures 2, A1, and A2: correlation scatterplots

```{r}
#figure 2, registered users
corr_reg <- train_reg %>% dplyr::select(user_rent, day_yr, season,  month, holiday, day_name, workday, 
                                        weather,  adj_tempF, humid, wind)
names(corr_reg) <- c("Rentals", "Day No.", "Season", "Month", "Holiday", "Day of Week", "Work Day", "Weather", "Temperature", "Humidity", "Wind Speed")
scat_reg <- ggpairs(corr_reg, 
                    upper = list(combo = wrap("box_no_facet", alpha=0.5, size=2),
                                 continuous = wrap("cor", size=2) ),
                    lower=list(combo=wrap("points", alpha=0.1, size=0.01 ),
                               continuous=wrap("points", alpha=0.1, size=0.01),
                               discrete=wrap("points", alpha=0.1, size=0.01) ),
                    diag = list(continuous = wrap("densityDiag", alpha = 0.5)), progress=F) +
  ggtitle("Scatterplots for Variables of Interest - Registered Users \n") +
  stdplot +
  theme(text= element_text(size = 3),
  axis.text = element_text( size=3), 
  axis.ticks = element_blank() )
scat_reg


#figure A1, casual users workdays
corr_cas_work <- train_cas_work %>% dplyr::select(user_rent, day_yr, season,  month,  day_name, 
                                        weather,  adj_tempF, humid, wind)
names(corr_cas_work) <- c("Rentals", "Day No.", "Season", "Month",  "Day of Week",  "Weather", "Temperature", "Humidity", "Wind Speed")
scat_cas_work <- ggpairs(corr_cas_work, 
                    upper = list(combo = wrap("box_no_facet", alpha=0.5, size=2),
                                 continuous = wrap("cor", size=2) ),
                    lower=list(combo=wrap("points", alpha=0.1, size=0.01 ),
                               continuous=wrap("points", alpha=0.1, size=0.01),
                               discrete=wrap("points", alpha=0.1, size=0.01) ),
                    diag = list(continuous = wrap("densityDiag", alpha = 0.5)), progress=F) +
  ggtitle("Scatterplots for Variables of Interest - Casual Users, Workdays \n") +
  stdplot +
  theme(text= element_text(size = 3),
  axis.text = element_text( size=3), 
  axis.ticks = element_blank() )
scat_cas_work


#Figure A2, casual users, nonworkdays
corr_cas_nowork <- train_cas_nowork %>% dplyr::select(user_rent, day_yr, season,  month,  day_name,  
                                        weather,  adj_tempF, humid, wind)
names(corr_cas_nowork) <- c("Rentals", "Day No.", "Season", "Month",  "Day of Week",  "Weather", "Temperature", "Humidity", "Wind Speed")
scat_cas_nowork <- ggpairs(corr_cas_nowork, 
                    upper = list(combo = wrap("box_no_facet", alpha=0.5, size=2),
                                 continuous = wrap("cor", size=2) ),
                    lower=list(combo=wrap("points", alpha=0.1, size=0.01 ),
                               continuous=wrap("points", alpha=0.1, size=0.01),
                               discrete=wrap("points", alpha=0.1, size=0.01) ),
                    diag = list(continuous = wrap("densityDiag", alpha = 0.5)), progress=F) +
  ggtitle("Scatterplots for Variables of Interest - Casual Users, Non-Workdays \n") +
  stdplot +
  theme(text= element_text(size = 3),
  axis.text = element_text( size=3), 
  axis.ticks = element_blank() )
scat_cas_nowork
```

## Final model with diagnostics - registered users

```{r}
#registered users
#base model
m2r <- lm(user_rent ~ day_yr + I(day_yr^2), data=train_reg)
#final model
mv1r <- update(m2r, .~ . + relevel(as.factor(season), ref=4) + workday + as.factor(weather) + adj_tempF + humid + wind )
mv2r <- update(mv1r, .~. + I(adj_tempF^2) + I(humid^2))

#diagnostics
anova( mv1r, mv2r)
AIC(mv1r)
AIC(mv2r)
VIF(mv2r)
#without quad terms - note season is factor so high
reg_vif <- update(mv2r, .~. -I(day_yr^2) - I(adj_tempF^2) - I(humid^2))
VIF(reg_vif)


#plots
fitted_reg         <- fitted(mv2r)
test_stanResLS_reg <- rstandard(mv2r)
test_dataLS_reg    <- data.frame(train_reg, test_stanResLS_reg, fitted_reg, train_reg$user_rent, train_reg$day_yr)

#force to zero for negative predictions
test_dataLS_reg$fitted_reg <- ifelse( fitted_reg <0, 0, fitted_reg)

#predicted v residual
pred_residual_reg <- ggplot(test_dataLS_reg, aes(x=fitted_reg, y=test_stanResLS_reg)) + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Predicted Rentals") +
  ylab("Standardized Residuals \n") +
  ggtitle("Predicted Rentals vs Residuals - Registered Users") +
  stdplot

#actual vs residual
actual_residual_reg <- ggplot(test_dataLS_reg, aes(x=train_reg$user_rent, y=test_stanResLS_reg))  + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Actual Rentals") +
  ylab("Standardized Residuals \n ") +
  ggtitle("Actual Rentals vs Residuals - Registered Users") +
  stdplot

resid_hist_reg <- ggplot(test_dataLS_reg, aes(x=test_stanResLS_reg)) + 
  geom_histogram(binwidth = 0.25, fill="steelblue4", color="steelblue4") +
  xlab("\n Standarized Residuals") +
  ylab("Number of Observations \n") +
  ggtitle("Distribution of Residuals - Registered Users") +
  stdplot

# QQplot
p_reg <- ggplot(data.frame(test_dataLS_reg), aes(sample = test_stanResLS_reg)) + stdplot
p_reg <- p_reg + stat_qq( color="steelblue4") + stat_qq_line(color="grey30") 

pred_residual_reg
actual_residual_reg
p_reg
resid_hist_reg
```

## Final model with diagnostics - casual users, workdays

```{r}
#base model
m2c_work <- lm(user_rent ~ day_yr + I(day_yr^2), data=train_cas_work)
#final model
mv1c_work <- update(m2c_work, .~.  + as.factor(weather) + adj_tempF, data=train_cas_work )
mv4c_work <- update(mv1c_work, .~.  + I(adj_tempF^2), data=train_cas_work ) 

#diagnostics
anova( mv1c_work, mv4c_work)
AIC(mv1c_work)
AIC(mv4c_work)
VIF(mv4c_work)
#without quad terms
casw_vif <- update(mv4c_work, .~. -I(day_yr^2) - I(adj_tempF^2) )
VIF(casw_vif)

#plots
fitted_cas_work         <- fitted(mv4c_work)
test_stanResLS_cas_work <- rstandard(mv4c_work)
test_dataLS_cas_work    <- data.frame(train_cas_work, test_stanResLS_cas_work, fitted_cas_work, train_cas_work$user_rent, train_cas_work$day_yr)
#force to zero for negative predictions
test_dataLS_cas_work$fitted_cas_work <- ifelse( fitted_cas_work <0, 0, fitted_cas_work)
 
#predicted v residual
pred_residual_cas_work <- ggplot(test_dataLS_cas_work, aes(x=fitted_cas_work, y=test_stanResLS_cas_work)) + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Predicted Rentals") +
  ylab("Standardized Residuals \n") +
  ggtitle("Predicted Rentals vs Residuals - Casual Users, Workdays") +
  stdplot

#actual vs residual
actual_residual_cas_work <- ggplot(test_dataLS_cas_work, aes(x=train_cas_work$user_rent, y=test_stanResLS_cas_work))  + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Actual Rentals") +
  ylab("Standardized Residuals \n ") +
  ggtitle("Actual Rentals vs Residuals - Casual Users, Workdays") +
  stdplot


resid_hist_cas_work <- ggplot(test_dataLS_cas_work, aes(x=test_stanResLS_cas_work)) + 
  geom_histogram(binwidth = 0.25, fill="steelblue4", color="steelblue4") +
  xlab("\n Standarized Residuals") +
  ylab("Number of Observations \n") +
  ggtitle("Distribution of Residuals - Casual Users, Workdays") +
  stdplot

# QQplot
p_cas_work <- ggplot(data.frame(test_dataLS_cas_work), aes(sample = test_stanResLS_cas_work)) + stdplot
p_cas_work <- p_cas_work + stat_qq( color="steelblue4") + stat_qq_line(color="grey30") 

pred_residual_cas_work
actual_residual_cas_work
resid_hist_cas_work
p_cas_work
```

## Final model with diagnostics - casual users, nonworkdays

```{r}
m2c_nowork <- lm(user_rent ~ day_yr + I(day_yr^2), data=train_cas_nowork)
mv1c_nowork <- update(m2c_nowork, .~.  + as.factor(weather) + adj_tempF + wind, data=train_cas_nowork )
mv4c_nowork <- update(mv1c_nowork, .~.  + I(adj_tempF^2), data=train_cas_nowork )
mv5c_nowork <- update(mv4c_nowork, .~. + (adj_tempF * wind), data=train_cas_nowork)
summary(mv5c_nowork)

#diagnostics
anova(mv1c_nowork, mv5c_nowork)
AIC(mv1c_nowork)
AIC(mv4c_nowork)
AIC(mv5c_nowork)
VIF(mv5c_nowork) 
#without quad terms
casnw_vif <- update(mv4c_nowork, .~. -I(day_yr^2) - I(adj_tempF^2)  )
VIF(casnw_vif)


#plots
fitted_cas_nowork         <- fitted(mv5c_nowork)
test_stanResLS_cas_nowork <- rstandard(mv5c_nowork)
test_dataLS_cas_nowork    <- data.frame(train_cas_nowork, test_stanResLS_cas_nowork, fitted_cas_nowork, train_cas_nowork$user_rent, train_cas_nowork$day_yr)
#force to zero for negative predictions
test_dataLS_cas_nowork$fitted_cas_nowork <- ifelse( fitted_cas_nowork <0, 0, fitted_cas_nowork)

#predicted vs residual
pred_residual_cas_nowork <- ggplot(test_dataLS_cas_nowork, aes(x=fitted_cas_nowork, y=test_stanResLS_cas_nowork)) + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Predicted Rentals") +
  ylab("Standardized Residuals \n") +
  ggtitle("Predicted Rentals vs Residuals - Casual Users, Non-Workdays") +
  stdplot

#actual vs residual
actual_residual_cas_nowork <- ggplot(test_dataLS_cas_nowork, aes(x=train_cas_nowork$user_rent, y=test_stanResLS_cas_nowork))  + 
  geom_point(size = 0.5, color="steelblue4") +
  geom_hline(yintercept=2,color='grey') + 
  geom_hline(yintercept=-2, color='grey') +
  geom_hline(yintercept=0, color="grey", linetype="dashed") +
  xlab("\n Actual Rentals") +
  ylab("Standardized Residuals \n ") +
  ggtitle("Actual Rentals vs Residuals - Casual Users, Non-Workdays") +
  stdplot

resid_hist_cas_nowork <- ggplot(test_dataLS_cas_nowork, aes(x=test_stanResLS_cas_nowork)) + 
  geom_histogram(binwidth = 0.25, fill="steelblue4", color="steelblue4") +
  xlab("\n Standarized Residuals") +
  ylab("Number of Observations \n") +
  ggtitle("Distribution of Residuals - Casual Users, Non-Workdays") +
  stdplot

# QQplot
p_cas_nowork <- ggplot(data.frame(test_dataLS_cas_nowork), aes(sample = test_stanResLS_cas_nowork)) + stdplot
p_cas_nowork <- p_cas_nowork + stat_qq( color="steelblue4") + stat_qq_line(color="grey30") 

pred_residual_cas_nowork
actual_residual_cas_nowork
resid_hist_cas_nowork
p_cas_nowork
```

## Validation analysis

```{r}
#registered users
res_train_reg <- resid(mv2r)            # residuals for training data
mse_train_reg <- mean(res_train_reg^2)  # mean squared error for training data
mse_train_reg

# residuals for validation data
output_reg  <- predict(mv2r, se.fit=TRUE, newdata=val_reg)
res_val_reg <- val_reg$user_rent - output_reg$fit

mse_val_reg <- mean(res_val_reg^2)  # mean squared error for validation data
rel_mse_val_reg <- mean(res_val_reg^2) / mean((val_reg$user_rent)^2)  # relative mean squared error for validation data
mse_val_reg
rel_mse_val_reg


#casual users workdays
# residuals for training data
res_train_work <- resid(mv4c_work)  

# mean squared error for training data
mse_train_work <- mean(res_train_work^2)
mse_train_work

# residuals for validation data
output_cas_work  <- predict(mv4c_work, se.fit=TRUE, newdata=val_cas_work)
res_val_cas_work <- val_cas_work$user_rent - output_cas_work$fit

# mean squared error for validation data
mse_val_cas_work <- mean(res_val_cas_work^2)
mse_val_cas_work

# relative mean squared error for validation data
rel_mse_val_cas_work   <- mean(res_val_cas_work^2) / mean((val_cas_work$user_rent)^2)
rel_mse_val_cas_work


#casual users nonworkdays
# residuals for training data
res_train_nowork <- resid(mv5c_nowork)

# mean squared error for training data
mse_train_nowork <- mean(res_train_nowork^2)
mse_train_nowork

# residuals for validation data
output_cas_nowork  <- predict(mv5c_nowork, se.fit=TRUE, newdata=val_cas_nowork)
res_val_cas_nowork <- val_cas_nowork$user_rent - output_cas_nowork$fit

# mean squared error for validation data
mse_val_cas_nowork <- mean(res_val_cas_nowork^2)
mse_val_cas_nowork

# relative mean squared error for validation data
rel_mse_val_cas_nowork <- mean(res_val_cas_nowork^2) / mean((val_cas_nowork$user_rent)^2)  
rel_mse_val_cas_nowork
```

## Validation plots observed vs. predicted - appendix A3, A4, A5

```{r}
# registered - create a data frame with validation observations and predictions
# create a data frame with validation observations and predictions
result_reg <- data.frame(val_reg$user_rent, output_reg$fit, val_reg$date)
colnames(result_reg)[1] <- "Observed"
colnames(result_reg)[2] <- "Predicted"
colnames(result_reg)[3] <- "Date"

# plot observations vs predictions
val_scatter_reg <- ggplot(result_reg, aes(x=Observed, y=Predicted)) +
  geom_point(size=0.5, color="steelblue4") +
  geom_abline(intercept=0, slope=1, color="indianred4", alpha=.6) +
  xlab("Observed Rentals")
  ggtitle("Validation: Predicted vs Observed Rentals (Registered)") +
  stdplot
val_scatter_reg

#casual workdays
# create a data frame with validation observations and predictions
result_cas_work <- data.frame(val_cas_work$user_rent, output_cas_work$fit, val_cas_work$date)
colnames(result_cas_work)[1] <- "Observed"
colnames(result_cas_work)[2] <- "Predicted"
colnames(result_cas_work)[3] <- "Date"

# plot observations vs predictions
val_scatter_cas_work <- ggplot(result_cas_work, aes(x=Observed, y=Predicted)) +
  geom_point(size=0.5, color="steelblue4") +
  geom_abline(intercept=0, slope=1, color="indianred4", alpha=0.6) +
  ggtitle("Validation: Predicted vs Observed Rentals (Casual, Workdays)") +
  stdplot
val_scatter_cas_work

#casual nonworkdays
result_cas_nowork <- data.frame(val_cas_nowork$user_rent, output_cas_nowork$fit, val_cas_nowork$date)
colnames(result_cas_nowork)[1] <- "Observed"
colnames(result_cas_nowork)[2] <- "Predicted"
colnames(result_cas_nowork)[3] <- "Date"

# plot observations vs predictions
val_scatter_cas_nowork <- ggplot(result_cas_nowork, aes(x=Observed, y=Predicted)) +
  geom_point(size=0.5, color="steelblue4") +
  geom_abline(intercept=0, slope=1, color="indianred4", alpha=0.6) +
  ggtitle("Validation: Predicted vs Observed Rentals (Casual, Non-workdays)") +
  stdplot
val_scatter_cas_nowork
```

## Validation plots observed and predicted over time, Figure 4

```{r}
#validation plots
#registered
valid_reg <- ggplot(result_reg, aes(x=Date, y=Observed, color="blue")) +
  geom_line() +
  geom_line(aes(x=result_reg$Date, y=result_reg$Predicted, color="red")) +
  #geom_point(size=0.5) +
 scale_x_date(date_breaks = "2 months",  date_labels = "%b %Y", limits = as.Date(c('2012-01-01','2012-012-31'))  )+
  scale_color_manual(name=element_blank(), labels=c("Observed \n2012", "Predicted \n2012"), values=c(   "indianred4", "steelblue4")) +
  xlab("\n Day of Year") +
  ylab("Rental Volume\n") +
  ggtitle("Validation on 2012 Data for Registered Users") +
  stdplot

#casual workdays
valid_cas_work <- ggplot(result_cas_work, aes(x=Date, y=Observed, color="blue")) +
  geom_line() +
  geom_line(aes(x=result_cas_work$Date, y=result_cas_work$Predicted, color="red")) +
  #geom_point(size=0.5) +
  scale_color_manual(name=element_blank(), labels=c("Observed \n2012", "Predicted \n2012"), values=c(   "indianred4", "steelblue4")) +
   scale_x_date(date_breaks = "2 months",  date_labels = "%b %Y", limits = as.Date(c('2012-01-01','2012-012-31'))  )+
  xlab("\n Day of Year") +
  ylab("Rental Volume \n") +
  theme(legend.key = element_blank() ,
        legend.title = element_text(size=5, color="#93a1a1"),
        legend.text = element_text(size=5, color="#93a1a1")) +
  ggtitle("Validation on 2012 Data for Casual Users - Workdays") +
  stdplot

#casual nonworkdays
valid_cas_nowork <- ggplot(result_cas_nowork, aes(x=Date, y=Observed, color="blue")) +
  geom_line() +
  geom_line(aes(x=result_cas_nowork$Date, y=result_cas_nowork$Predicted, color="red")) +
  #geom_point(size=0.5) +
  scale_color_manual(name=element_blank(), labels=c("Observed \n2012", "Predicted \n2012"), values=c(   "indianred4", "steelblue4")) +
   scale_x_date(date_breaks = "2 months",  date_labels = "%b %Y", limits = as.Date(c('2012-01-01','2012-012-31'))  )+
  xlab("\n Day of Year") +
  ylab("Rental Volume \n") +
  theme(legend.key = element_blank() ,
        legend.title = element_text(size=5, color="#93a1a1"),
        legend.text = element_text(size=5, color="#93a1a1")) +
  ggtitle("Validation on 2012 Data for Casual Users - Non-Workdays") +
  stdplot

valid_reg
valid_cas_nowork
valid_cas_work
```

## Standardized coefficients and tables

```{r}
std_border <- fp_border(color="black", style="solid", width=1)

#registered Table 1
regstd <-lm.beta::lm.beta(mv2r)
x <- round(as.data.frame(summary(mv2r)$coefficients), 3) #pull estimates, t stat and p value
a <- round(as.data.frame(confint(mv2r) ), 3)  #create CI
b <- round(as.data.frame(regstd$standardized.coefficients), 3)
est_names <-  c("Estimate", "LCL", "UCL", "Std Coeff", "t value", "Pr(>|t|)")
base_vars <- c("Intercept", "Day No.", "Day No. ^2", "Spring", "Summer", "Fall", "Work Day", "Poor Weather", "Very Poor Weather", "Temperature F", "Humidity", "Windspeed", "Temp ^2", "Humidity ^2")
base_temp <- cbind(x, a, b)
base_est <- as.data.frame(cbind(base_temp[,1], base_temp[,5:7], base_temp[,3:4])) #rearrange columns with CI after est
names(base_est) <- est_names
row.names(base_est) <- base_vars
base_est <- base_est[c(1:10, 13, 11, 14, 12),]
base_reg_ft <- autofit(flextable(base_est %>% rownames_to_column("Variable"))) %>%
               set_caption("Table 1, Point Estimates for Final Model - Registered Users") %>%
               bg(bg="lightsteelblue1",part="header") %>%
               bold(part="header") %>%
               bold(i= ~ base_est[,6] < 0.05, j=7 ) %>%
               color(i= ~ base_est[,6] < 0.05, j=7, color="coral4", part="body" ) %>%
               fontsize(size=10, part="body") %>%
               fontsize(size=10, part="header") %>%
               hline(i=1, part="body", border = std_border)
base_reg_ft

#casual workdays Table 2
caswstd <-lm.beta::lm.beta(mv4c_work)
x <- round(as.data.frame(summary(mv4c_work)$coefficients), 3) #pull estimates, t stat and p value
a <- round(as.data.frame(confint(mv4c_work) ), 3)  #create CI
b <- round(as.data.frame(caswstd$standardized.coefficients), 3)
est_names <-  c("Estimate", "LCL", "UCL", "Std Coeff", "t value", "Pr(>|t|)")
base_vars <- c("Intercept",  "Day No.", "Day No. ^2", "Poor Weather", "Very Poor Weather", "Temperature F", "Temp ^2")
base_temp <- cbind(x, a, b)
base_est <- as.data.frame(cbind(base_temp[,1], base_temp[,5:7], base_temp[,3:4])) #rearrange columns with CI after est
names(base_est) <- est_names
row.names(base_est) <- base_vars
#base_est <- base_est[c(1:10, 13, 11, 14, 12),]
base_casw_ft <- autofit(flextable(base_est %>% rownames_to_column("Variable"))) %>%
               set_caption("Table 2, Point Estimates for Final Model - Casual Users, Workdays") %>%
               bg(bg="lightsteelblue1",part="header") %>%
               bold(part="header") %>%
               bold(i= ~ base_est[,6] < 0.05, j=7 ) %>%
               color(i= ~ base_est[,6] < 0.05, j=7, color="coral4", part="body" ) %>%
               fontsize(size=10, part="body") %>%
               fontsize(size=10, part="header") %>%
               hline(i=1, part="body", border = std_border)
base_casw_ft

#casual non-workdays Table 3
casnwstd <-lm.beta::lm.beta(mv5c_nowork)
x <- round(as.data.frame(summary(mv5c_nowork)$coefficients), 3) #pull estimates, t stat and p value
a <- round(as.data.frame(confint(mv5c_nowork) ), 3)  #create CI
b <- round(as.data.frame(casnwstd$standardized.coefficients), 3)
est_names <-  c("Estimate", "LCL", "UCL", "Std Coeff", "t value", "Pr(>|t|)")
base_vars <- c("Intercept", "Day No.", "Day No. ^2",  "Poor Weather", "Very Poor Weather", "Temperature F", "Wind Speed",  "Temp ^2",  "Temp*Wind")
base_temp <- cbind(x, a, b)
base_est <- as.data.frame(cbind(base_temp[,1], base_temp[,5:7], base_temp[,3:4])) #rearrange columns with CI after est
names(base_est) <- est_names
row.names(base_est) <- base_vars
base_est <- base_est[c( 1:6, 8, 7, 9),]
base_casnw_ft <- autofit(flextable(base_est %>% rownames_to_column("Variable"))) %>%
               set_caption("Table 3, Point Estimates for Final Model - Casual Users, Non-Workdays") %>%
               bg(bg="lightsteelblue1",part="header") %>%
               bold(part="header") %>%
               bold(i= ~ base_est[,6] < 0.05, j=7 ) %>%
               color(i= ~ base_est[,6] < 0.05, j=7, color="coral4", part="body" ) %>%
               fontsize(size=10, part="body") %>%
               fontsize(size=10, part="header") %>%
               hline(i=1, part="body", border = std_border)
base_casnw_ft
```

